---
title: "PF Velcoity calc"
author: "Josh Norman"
date: "2026-01-09"
output: html_document
---

1. Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)
```

# 2. Required libraries

```{r libraries, echo=FALSE}
library(tidyverse)
library(gt)
library(kableExtra)
library(ggbreak)
library(cowplot)
library(ggpubr)
```

# 4. Import data

```{r delineated_list, echo=FALSE}
#Get all delineated files
delineated_file_list <- list.files("C:/users/591302/OneDrive - hull.ac.uk/FSE Hull International Fisheries Institute - Documents/REDEEM 2.0/
                                   HS_JOSH_NORMAN/RAPID_processing/processed_sens_data/csv/delineated/", 
                                   pattern = "_delineated\\.csv$", full.names = TRUE)
#Get all sensor data files
full_sens_file_list <- list.files("C:/users/591302/OneDrive - hull.ac.uk/FSE Hull International Fisheries Institute - Documents/REDEEM 2.0/
                                  HS_JOSH_NORMAN/RAPID_processing/processed_sens_data/csv/",
                                  pattern = "\\.csv$", full.names = TRUE)

# Remove any files appended with _min
full_sens_file_list <- full_sens_file_list[!grepl("_min\\.csv$", full_sens_file_list)]

```


```{r data}
#Main index data
sensor_index <- read_csv("./shiny/processed_sens_data/index/global_sensor_index.csv")
instrument_index <- read_csv("./shiny/processed_sens_data/instrument_data/global_processed_instrument_data.csv")

#Pump flow meta data
pf_meta <- read_csv("./shiny/processed_sens_data/PumpFlow META/all_pro_rapid_data.csv")

```

1. Filter data to just pumpflow data, so only need delineated and full sensor files where sensor_index 'deployment' == PF_Test_Rig_2024
2. For each unique 'file' in the filtered sensor_index, find the associated _delineated file
3. In each _delineated file, filter to only copntain 'roi' == roi4_nadir
4. Using the associated time_s data for each sensors (roi 4 only), retrieve the associated full sensor file and extract the rows corrosponding to the time_s
5. Filter this data to only contain the columns time_s	higacc_x_g	higacc_y_g	higacc_z_g	higacc_mag_g
6. bind all sensor data into new dataframe 'pf_roi4_hig_3axis'


# 5. Clean, merge, typeset
